---
title: "Posterior for $f$ and posterior predictive distribution"
author: "Haziq Jamil"
date: "01/04/2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
knitr::read_chunk("01-prelim.R")
knitr::read_chunk("02-iprior-plots.R")
knitr::read_chunk("03-GPR-plots.R")
```

```{r prelim, include = FALSE}
```
```{r points, include = FALSE}
```
```{r plot.function.gpr, include = FALSE}
```
```{r plot.function.iprior, include = FALSE}
```

# Comparison between I-prior and Gaussian Process priors

\newpage

# Canonical kernel

```{r canonical.kernel, include = FALSE, cache = TRUE}
```
```{r canonical.kernel.iprior, include = FALSE, cache = TRUE}
```

#### Prior and posterior draws (GPR)

```{r, echo = FALSE, warning = FALSE, fig.height = 8.3, fig.width = 7, out.width = "18cm"}
plot.can$p4
```

\newpage

#### Prior and posterior draws (I-prior)

```{r, echo = FALSE, warning = FALSE, fig.height = 8.3, fig.width = 7, out.width = "18cm"}
plot.can.iprior$p4
```

\newpage

#### 95% posterior predictive bands (GPR)

```{r, echo = FALSE, warning = FALSE, out.height = "10cm"}
plot.can$p3
```

#### 95% posterior predictive bands (I-prior)

```{r, echo = FALSE, warning = FALSE, out.height = "10cm"}
plot.can.iprior$p3
```






# FBM kernel

```{r fbm.kernel, include = FALSE, cache = TRUE}
```
```{r fbm.kernel.iprior, include = FALSE, cache = TRUE}
```

#### Prior and posterior draws (GPR)

```{r, echo = FALSE, warning = FALSE, fig.height = 8.3, fig.width = 7, out.width = "18cm"}
plot.fbm$p4
```

\newpage

#### Prior and posterior draws (I-prior)

```{r, echo = FALSE, warning = FALSE, fig.height = 8.3, fig.width = 7, out.width = "18cm"}
plot.fbm.iprior$p4
```

\newpage

#### 95% posterior predictive bands (GPR)

```{r, echo = FALSE, warning = FALSE, out.height = "10cm"}
plot.fbm$p3
```

#### 95% posterior predictive bands (I-prior)

```{r, echo = FALSE, warning = FALSE, out.height = "10cm"}
plot.fbm.iprior$p3
```







# Squared Exponential kernel

```{r se.kernel, include = FALSE, cache = TRUE}
```
```{r se.kernel.iprior, include = FALSE, cache = TRUE}
```

#### Prior and posterior draws (GPR)

```{r, echo = FALSE, warning = FALSE, fig.height = 8.3, fig.width = 7, out.width = "18cm"}
plot.se$p4
```

\newpage

#### Prior and posterior draws (I-prior)

```{r, echo = FALSE, warning = FALSE, fig.height = 8.3, fig.width = 7, out.width = "18cm"}
plot.se.iprior$p4
```

\newpage

#### 95% posterior predictive bands (GPR)

```{r, echo = FALSE, warning = FALSE, out.height = "10cm"}
plot.se$p3
```

#### 95% posterior predictive bands (I-prior)

```{r, echo = FALSE, warning = FALSE, out.height = "10cm"}
plot.se.iprior$p3
```
